Spatial variation of coronal Fourier power spectra

### 2016-08-15 tex/paper2/paper2.tex
better plots with the new fitting

\begin{figure}
\label{fig:spatialdistribution:preference}
\centerline{
\epsscale{0.8}\plottwo{spatial_distrib.paper2_six_euv_disk_1.5_171_six_euv.BIC.6.0.with_mask.eps}{spatial_distrib.paper2_six_euv_disk_1.5_131_six_euv.BIC.6.0.with_mask.eps}
}
\centerline{
\epsscale{0.8}\plottwo{spatial_distrib.paper2_six_euv_disk_1.5_171_six_euv.BIC.6.0.with_mask.eps}{spatial_distrib.paper2_six_euv_disk_1.5_193_six_euv.BIC.6.0.with_mask.eps}
}
\centerline{
\epsscale{0.8}\plottwo{spatial_distrib.paper2_six_euv_disk_1.5_211_six_euv.BIC.6.0.with_mask.eps}{spatial_distrib.paper2_six_euv_disk_1.5_335_six_euv.BIC.6.0.with_mask.eps}
}
\caption{Spatial distribution of model preference. Blue pixels indicate a strong preference for Model 2.  Cyan pixels indicate a strong preference for Model 1.  Black pixels indicate that neither Model 1 or Model 2 could be fit to the data. The remaining pixels show a weaker preference for either Model 1 or Model 2.  The location of the sunspot is indicated by the white contour.}
\end{figure}

\begin{figure}
\label{fig:spatialdistribution:powerlawindex}
\centerline{
\epsscale{0.8}\plottwo{paper2_six_euv_disk_1.5_94.exact_map.six_euv.eps}{paper2_six_euv_disk_1.5_131.exact_map.six_euv.eps}
}
\centerline{
\epsscale{0.8}\plottwo{paper2_six_euv_disk_1.5_171.exact_map.six_euv.eps}{paper2_six_euv_disk_1.5_193.exact_map.six_euv.eps}
}
\centerline{
\epsscale{0.8}\plottwo{paper2_six_euv_disk_1.5_211.exact_map.six_euv.eps}{paper2_six_euv_disk_1.5_335.exact_map.six_euv.eps}
}
\caption{Spatial distribution of the power law indices.  Power law
  indices are taken from either model $M_{1}$ or $M_{2}$, whichever
  model is preferred at each pixel (see Section \ref{sec:anal})}
\end{figure}

\begin{figure}
\label{fig:spatialdistribution:gaussianposition}

>>>>

\begin{figure}
\label{fig:spatialdistribution:preference}
\centerline{
\epsscale{0.8}\plottwo{spatial_distrib.paper2_six_euv_disk_1.5_171_six_euv.BIC.6.0.with_mask.eps}{spatial_distrib.paper2_six_euv_disk_1.5_193_six_euv.BIC.6.0.with_mask.eps}
}
\centerline{
\epsscale{0.8}\plottwo{spatial_distrib.paper2_six_euv_disk_1.5_211_six_euv.BIC.6.0.with_mask.eps}{spatial_distrib.paper2_six_euv_disk_1.5_335_six_euv.BIC.6.0.with_mask.eps}
}
\centerline{
\epsscale{0.8}\plottwo{spatial_distrib.paper2_six_euv_disk_1.5_94_six_euv.BIC.6.0.with_mask.eps}{spatial_distrib.paper2_six_euv_disk_1.5_131_six_euv.BIC.6.0.with_mask.eps}
}
\caption{Spatial distribution of model preference. Blue pixels indicate a strong preference for Model 2.  Cyan pixels indicate a strong preference for Model 1.  Black pixels indicate that neither Model 1 or Model 2 could be fit to the data. The remaining pixels show a weaker preference for either Model 1 or Model 2.  The location of the sunspot is indicated by the white contour.}
\end{figure}

\begin{figure}
\label{fig:spatialdistribution:powerlawindex}
\centerline{
\epsscale{0.8}\plottwo{spatial.common.171.powerlawindex.six_euv.standard.eps}{spatial.common.193.powerlawindex.six_euv.standard.eps}
}
\centerline{
\epsscale{0.8}\plottwo{spatial.common.211.powerlawindex.six_euv.standard.eps}{spatial.common.335.powerlawindex.six_euv.standard.eps}
}
\centerline{
\epsscale{0.8}\plottwo{spatial.common.94.powerlawindex.six_euv.standard.eps}{spatial.common.131.powerlawindex.six_euv.standard.eps}
}
\caption{Spatial distribution of the power law indices.  Power law
  indices are taken from either model $M_{1}$ or $M_{2}$, whichever
  model is preferred at each pixel (see Section \ref{sec:anal})}
\end{figure}

\begin{figure}
\label{fig:spatialdistribution:gaussianposition}
\centerline{
\epsscale{0.8}\plottwo{spatial.within.171.lognormalposition.PowerLaw+Constant+Lognormal.six_euv.BIC.ge.6.000000.standard.eps}{spatial.within.193.lognormalposition.PowerLaw+Constant+Lognormal.six_euv.BIC.ge.6.000000.standard.eps}
}
\centerline{
\epsscale{0.8}\plottwo{spatial.within.211.lognormalposition.PowerLaw+Constant+Lognormal.six_euv.BIC.ge.6.000000.standard.eps}{spatial.within.335.lognormalposition.PowerLaw+Constant+Lognormal.six_euv.BIC.ge.6.000000.standard.eps}
}
\centerline{
\epsscale{0.8}\plottwo{spatial.within.94.lognormalposition.PowerLaw+Constant+Lognormal.six_euv.BIC.ge.6.000000.standard.eps}{spatial.within.131.lognormalposition.PowerLaw+Constant+Lognormal.six_euv.BIC.ge.6.000000.standard.eps}
}
